### 2014-11-13 tex/intro.tex
blah blah

Initial work on symbolic execution largely focused on checking 
properties of programs with primitive types~\cite{clarke76TSE,King:76}.
%, e.g., integers and booleans 
%Despite recent advances
%in constraint solving technologies, improvements in
%raw computing power, and advances in reduction
%and abstraction techniques~\cite{AnandETAL2009AbsSymExe,Godefroid:POPL07}
%symbolic execution of programs of modest size containing only
%primitive types, remains challenging
%because of the large number of execution paths generated
%during symbolic analysis. 
With the advent of object-oriented languages,
% e.g., Java and C$++$, 
recent work has generalized the core ideas of symbolic execution to enable 
analysis of programs containing complex data structures with unbounded 
domains, i.e., data stored on the heap~\cite{Kiasan06,Kiasan07,GSE03}.  
These \emph{Generalized Symbolic Execution} (GSE) techniques construct the 
heap in a lazy manner, deferring
materialization of objects on the concrete heap until they are needed
for the analysis to proceed. The materilization 
%accounts for various heap configurations, 
creates additional non-deterministic choice points in the symbolic
execution tree by representing the feasible heap configurations as (i)
null, (ii) an instance of a new reference of a compatible class, and (iii)
an alias to a previously initialized symbolic reference.  Symbolic
execution then follows concrete program semantics for materialized heap
locations. Although this approach enables the analysis of heap
manipulating programs, a large number of feasible concrete heap
configurations are created leading to state space explosion.

%  resulting in a large number of feasible concrete heap
%configurations, and as a result, a large number of points of
%non-determinism to be analyzed.
%, further exacerbating the state space
%explosion problem.

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. Our
inspiration is found in the domain of static analysis that uses sets
of constraints over heap locations to encode multiple heaps in a
single representation. These sets, sometimes known as \emph{value
  sets} or \emph{value summaries}, allow multiple heaps to be
represented simultaneously with a higher degree of precision than
afforded by traditional techniques for shape analysis. Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{Xie:2005}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static analysis, over
approximation of the heap representations alleviates some of these
limitations but also leads to infeasible heaps. Also, heap updates
require a rewrite of the constraint system making it prohibtive for use
in the context of symbolic execution.

>>>>

Initial work on symbolic execution largely focused on checking
properties of programs with primitive
types~\cite{clarke76TSE,King:76}.  With the advent of object-oriented
languages, recent work has generalized the core ideas of symbolic
execution to enable analysis of programs containing complex data
structures with unbounded domains, i.e., data stored on the
heap~\cite{Kiasan06,Kiasan07,GSE03}.  These \emph{Generalized Symbolic
  Execution} (GSE) techniques construct the heap in a lazy manner,
deferring materialization of objects on the concrete heap until they
are needed for the analysis to proceed. The materilization creates
additional non-deterministic choice points in the symbolic execution
tree by representing the feasible heap configurations as (i) null,
(ii) an instance of a new reference of a compatible class, and (iii)
an alias to a previously initialized symbolic reference.  Symbolic
execution then follows concrete program semantics for materialized
heap locations. Although this approach enables the analysis of heap
manipulating programs, a large number of feasible concrete heap
configurations are created leading to a path explosion.

The goal of this work is to mitigate the path explosion problem in GSE
by grouping multiple heaps together and only partitioning the heaps at
points of divergence in the control flow graph. Our inspiration is
found in the domain of static analysis that uses sets of constraints
over heap locations to encode multiple heaps in a single
representation. These sets, sometimes known as \emph{value sets} or
\emph{value summaries}, allow multiple heaps to be represented
simultaneously with a higher degree of precision than afforded by
traditional techniques for shape analysis. Some of these previous
attempts, however, are unable to handle aliasing in heaps due to a
recursive definition of objects~\cite{Xie:2005}, while others require
a set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static
analysis, over approximation of the heap representations alleviates
some of these limitations but often leads to infeasible heaps. Also,
heap updates require a rewrite of the constraint system making it
prohibtive for use in the context of symbolic execution.
